MixEth: efficient, trustless coin mixing service for Ethereum

### 2019-01-09 article/main.tex
FC19 Reviews added

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. Expect further improvements. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&TBD&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table}

>>>>

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. Expect further improvements. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table}
